---
title: "R Week 5 Assignment Mikhail Groysman 09.23.2018"
author: "Mikhail Groysman"
date: "September 23, 2018"
output: html_document
---

Let's read csv file

```{r}

adata<-read.csv(file="C://Data/AirlinesData.csv")

adata
```
Let's get rid of a blank row and properly name first 2 columns

Let's load libraries tidyr and dplyr and then run fill function to populate missing values

```{r}

adata<-subset(adata,!is.na(Los.Angeles))

names(adata)[1:2]<-c("Airline","Status_flight")

# install.packages(c("tidyr","dplyr"))

library("tidyr")

library("dplyr")

adata$Airline[adata$Airline==""] <- NA

adata1<-adata %>% fill(Airline)

```

Now, we can transpose the dataframe. We could also reformat new column "Destination" to replace "." with " ". We will aslo spread Status_flight column

```{r}

adata2 <- adata1 %>% gather(Destination, Num_flights, -c("Airline","Status_flight"))

adata2$Destination <- gsub("\\.", " ", adata2$Destination)

adata3 <- adata2 %>% spread(Status_flight, Num_flights)

adata3
```

Let's rename column "on time" and resort our data.

```{r}

names(adata3)[4]<-c("on_time")

adata3

adata4<-adata3 %>% arrange(Airline, Destination)

adata4

```

Let's perform our analysis

```{r}

adata4$ratio<-round(adata4$delayed/(adata4$delayed+adata4$on_time),digits=2)

adata4

a_sum <- adata4 %>% group_by(Airline) %>% summarize(sumd=sum(delayed),sumon=sum(on_time))

a_sum

a_sum$ratio <- round(a_sum$sumd/(a_sum$sumon+a_sum$sumd),digits=2)

a_sum

```

Conclusion - Alaska company has more delayed flights than AM West


